\documentclass[letterpaper,10pt,serif,draftclsnofoot,onecolumn,compsoc,titlepage]{IEEEtran}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          
\usepackage{cite}
\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{pgfgantt}
\usepackage{rotating}
\usepackage{enumitem}
\usepackage{gensymb}
\usepackage[T1]{fontenc}

\usepackage{balance}
\usepackage[TABBOTCAP, tight]{subfigure}
\usepackage{enumitem}

\usepackage{geometry}
\geometry{margin=.75in}
\usepackage{hyperref}
\usepackage{breakurl}
%\usetikzlibrary{shapes, positioning, calc}
\usepackage{caption}
\usepackage{listings}
%\usepackage[utf8]{inputenc}
%pull in the necessary preamble matter for pygments output

%% The following metadata will show up in the PDF properties
\hypersetup{
   colorlinks = true,
   citecolor = black,
   linkcolor = black,
   urlcolor = black,
   breaklinks = true,
   pdfauthor = {Shu-Ping Chien, Brock Smedley, W Keith Striby Jr},
   pdfkeywords = {CS461 "Senior Project" Progress Report},
   pdftitle = {CS461 Progress Report},
   pdfsubject = {CS461 Progress Report},
   pdfpagemode = UseNone
}

\parindent = 0.0 in
\parskip = 0.1 in
\title{Progress Report: Multi-Camera, SoM Based, Real-Time Video Processing for UAS and VR/AR Applications}
\author{Area 51: Shu-Ping Chien, Brock Smedley, W Keith Stirby Jr \\ 04 December 2017 \\ CS461, Senior Software Engineering Project, Fall 2017}


\begin{document}
\begin{titlepage}
\maketitle

\begin{abstract}

This document highlights the group's progress made during the Fall 2017 term. The 
project is introduced along with an explanation of the hardware and software 
surrounding our product's planned solution. Each week of the Fall 2017 term is 
summarized along with a retrospective. \\

\thispagestyle{empty}
\end{abstract}
\end{titlepage}

\newpage
\tableofcontents

\newpage

\section{Introduction}

\subsection{Purpose}

Our project is required to provide a video output at near real-time from a 
multi-camera input utilizing an NVIDIA Jetson TX1 or TX2 system-on-module (SoM). 
The software produced will perform image processing and edge computing on the 
camera input to display a visually enhanced and stitched video output. 
Size, weight, power, and cost (SWaP-C) requirements for the project are due 
to its application being for UAS and VR/AR, and from our system utilizing a 
mass-produced SoM, particularly the Jetson TX1 or TX2.  

\subsection{Scope}
 
SHU-Ping or BROCK - PLEASE WRITE
Software scope/requirements here. (Take pixel streams, do the 
hokey pokey, and we have low latency, wicked fast video at near real-time speed.)
 
Application specific hardware and software are vital for the project due the the 
system requirements and constraints of the project.
The NVIDIA Jetson TX1 and TX2 run on an Ubuntu based Linux for Tegra (L4T) operating 
system created specifically for producing customized imaging, installed on a 
GPU-accelerated dual-core CPU with dual Image Signal Processors (ISPs). 
NVIDIA provides the Jetson Software Development Pack (JetPack) 3.1 which has L4T 28.1 
and is capable of supporting a multitude of multimedia and image processing API. 
The cameras will utilize the most widely used camera interface for mobile applications, 
MIPI CSI-2, which is capable of supporting 1080p, 4k, and 8k video. 
A carrier board will connect the cameras to the Jetson TX1 or TX2 that also provides 
additional application-specific interfaces and peripherals. \\

The software materials for this project will support the NVIDIA Jetson TX1 and TX2 and 
be able to produce fused images from cameras in near real-time. The media inputs from 
cameras through CSI will be captured in pipelines for distribution and transformation 
then sent to the image processor, and the process avoids to reload our input datas to 
reduce latency. The image processing software will utilize the images from media stream 
and produce stitched images as output to the display device.  \\


\subsection{Overview}

This document provides a recap of the progress made on our project during the 
Fall 2017 term. 
In addition to completing required documents and assignments the group primarily 
researched on hardware and software solutions necessary to complete the project 
successfully. Once hardware research was completed and procurement started the group 
began researching more into the design and development of software. The following 
sections reflect this progress with detailed weekly summaries and retrospectives. \\

\section{Week 1}

\subsection{Summary}

The first week of the term project choices were presented and preferences were
submitted. No project specific progress was made. \\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   N/A 
   & N/A 
   & N/A \\
   \hline
\end{tabular}

\section{Week 2}

\subsection{Summary}

The group was assigned the project specified and immediately began coordinating 
with the project's client, Carlo Tiana of Rockwell Collins. 
An email was written to Tiana to make first contact, exchange contact 
information,
established preferred contact medium, and began inquiring about our first meeting.
Introductions began with the group for each other to become acquainted with 
each other. 
The group shared their schedules on Google Calendar with each other and Tiana 
to coordinate weekly meetings for the term. 
Preliminary research on the NVIDIA Jetson TX1 and TX2 module, real-time video 
processing, and processing multispectral camera systems was performed by group members 
to prepare for the meeting scheduled with Tiana on Monday of Week 3. \\


\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   The group was assigned to the project and members were introduced to one another. 
   Contact was initiated with the project's client and a meeting was scheduled. 
   Research began on the topics surrounding the project's title to prepare 
   for our initial meeting occurring next week. 
   & 
   Nothing needed to be changed before the first meeting. The group would have the outline 
   and goal of the project next week. 
   & 
   After the first meeting with client, the group would start to work based on the content 
   of the meeting. \\
   \hline
\end{tabular}


\section{Week 3}

\subsection{Summary}

An initial meeting was held with the client Tiana a principle engineer and expert 
in aviation vision systems, and Weston Lahr, a software engineer 
for Rockwell Collins on Monday. Initial introductions occurred between the group, 
Tiana, and Lahr. 
Tiana presented to the group background information on the motivation for the project, 
provided a more elaborate description of what is expected of the group's product, and 
established objectives for the course of the project. The group inquired about 
information required to be answered in the Problem Statement document during the meeting 
as well. \\

Following the meeting the group began researching project details explained by Tiana 
and Lahr. Due to concerns regarding hardware acquisition expressed by Tiana, the group 
began researching system components required to satisfy the project's objectives. 
Project details surrounding the product's preferred SoM being the Jetson TX1 or TX2, 
the group researched the module and potential carrier boards that support a MIPI 
CSI-2 specification, as required for the project. \\

The group created a dedicated Google Drive directory to share project documents and 
research with Tiana and Lahr. A GitHub repository was created and shared to 
collaborate required documents among group members. 
Inquiries were made by the group regarding potential meeting locations on campus.
The Problem Statement draft was 
written. The group had an initial meeting with their TA, Daniel Lin, and meetings 
were scheduled to occur every Friday afternoon for the Fall Term.\\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   An initial meeting was held with the client Tiana, and Lahr who is a software 
   engineer with Rockwell Collins. Project details, motivations, and expectations 
   were established, and research began for the group based on the information learned. 
   Emails were exchanged between the group and Tiana regarding plans moving forward. 
   Hardware research was initiated based on project requirements, specifications, and 
   contraints. The main hardware components consists of the SoM, a carrier board with 
   the MIPI CSI-2 interface, and CSI-2 cameras. 
   The group began drafting the Problem Statement and emailed questions 
   to Tiana to obtain answers needed to write the document. 
   & 
   Although the hardware research was asked for both potential modules and carrier boards, 
   the range was too broad to research on since the group had minimal experience with the relevant hardware. 
   Therefore, the research range was expected to be focused on specific hardware.
   & 
   The TA Lin suggested to direct efforts toward carrier board research based on NVIDIA Jetson TX1 and TX2 at beginning, so the group would be able to get familiar with the system of the application. \\
   \hline
\end{tabular}

\subsection{Summary}

\section{Week 4}

\subsection{Summary}

Research continued on topics surrounding the project which includes: the Jetson TX1 and 
TX2, carrier boards with a MIPI CSI-2 interface compatible with the TX1 and TX2 
capable of supporting multiple cameras, image processing at real-time, software support 
for the TX1 and TX2, the MIPI CSI-2 standard, and cameras with a MIPI CSI-2 interface. \\

The group continued to write their Problem Statement which involved: researching 
examples from previous Capstone Projects, obtaining feedback from the writing center 
on campus, and emailing questions to Tiana. 
The Problem Statement was submitted for review to the professors and client once 
complete. \\

The NVIDIA Jetson TX2 module and development kit was obtained from Kevin McGrath for 
the group to begin setting up the module.
A meeting was scheduled with Tiana and the group for Tuesday of Week 5 and the weekly 
meeting with Lin occurred on Friday.\\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   The group acquired the Jetson TX2 module and development kit from McGrath. 
   Emails were exchanged between the group, Tiana, and McGrath regarding hardware 
   research for procurement. Tiana provided feedback on the Problem Statement 
   and approved the document. 
   & 
   In order to meet concrete goal of the project, the group needed some measurable datas of 
   requirements. 
   & 
   The second meeting with the client was reserved on the following Tuesday, so the group 
   would check the current process and problems with the client. \\
   \hline
\end{tabular}

\section{Week 5}

\subsection{Summary}

The group's second meeting was held with Tiana on Tuesday of Week 5. The meeting was 
virtual and the topics were: feedback from Tiana regarding the Problem Statement, 
hardware for the project was discussed and Tiana presented some carrier board information 
to assist our research, and the group asked about information necessary to complete 
the Requirements Document. \\

Based off Tiana's information discussed during the meeting regarding carrier boards,
more research was conducted. Potential carrier boards were identified and three 
were selected to be ordered. Additional hardware was selected to support those three 
carrier board selection and includes cameras, cables, port converters, and 
motherboards. The group coordinated with McGrath to order all 
hardware. \\

The group wrote and submitted their rough draft for the Requirements Document. The 
document was written based on information from meetings with Tiana, email 
communicaitons between the group and Tiana, and hardware research.  The group had 
their weekly Friday meeting with Lin. \\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   During the meeting with Tiana it was established that meetings would occur virtually 
   every other week for the remainder of the term. The group learned a lot more about 
   the desired carrier board and the features it should have. Based on the information 
   learned from research on carrier boards, the group identified three boards to be ordered. Additional 
   supporting hardware and the three carrier boards were requested to be 
   procured.  
   & 
   Based on the given carrier board (J106) from the client, the group was expected to do 
   research for the connection between the carrier board and module. 
   With the procured NVIDIA Jetson TX2, the group was able to set up the development 
   environment for the module. 
   & 
   The group planned to do research on the connection and functionality of carrier through 
   MIPI CSI-2 to ensure the output format and if it supported the project. 
   The group connected the NVIDIA Jetson TX2 module to Ubuntu and installed NVIDIA Jetpack 
   for developing on operating system and software.  \\
   \hline
\end{tabular}

\section{Week 6}

\subsection{Summary}

Completing the Requirements Document was the group's primary concern due to the 
final draft needing to be submitted on Friday of Week 6. Requested feedback 
from Tiana and McGrath before submitting the final draft. The group continued to 
work on the Requirements Document through the weekend. \\

It was confirmed by McGrath that hardware for the project had been ordered. The group 
had their weekly Friday meeting with Lin. \\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   Hardware ordering had began. The following carrier boards were ordered: the Auvidea 
   J106, Colorado Engineering Inc's X-Carrier, and the Connect Tech Inc Spacely Carrier. 
   For the X-Carrier an Auvidea J20 board was ordered to interface the MIPI CSI-2 
   cameras. To extend potential interfaces on the J106 the M100 and M110 motherboards 
   were ordered. Six Raspberry Pi V2 Cameras, cables, and pin converters were ordered 
   to connect with the J106 and X-Carrier. The Requirements Document was approved by 
   Tiana.
   & 
   Since the potential hardware pieces were determined, the group started to look forward 
   on the software for image processing. 
   The group needed to figure out how to transform multiple video inputs from cameras 
   through CSI to the image processor in near real-time. 
   In order to research on enough details for each technology, the group needed to determine 
   topics and distribute them to each group member.
   & 
   The research for software began based on the chosen hardware, and the group was also 
   starting to work on concrete operation for the project and technology review document. \\
   \hline
\end{tabular}

\section{Week 7}

\subsection{Summary}

The Requirements Document was submitted following feedback from Tiana and McGrath, 
and work immediately began on the Technology Review. The group collaborated on 
technologies involved in the project and divided up three technologies for each 
group member to research and report on. The weekly meeting with Lin did not happen 
due to Veteran's Day Holiday. Instead the group communicated with Lin via email. \\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   The Technology Review document involved a lot of research regarding what is in 
   store for the group for the remainder of the project. Each member was assigned a portion of the project that they were to be responsible for, and conducted research on the best technologies and methods to use for the project. 
   & 
   Following the completion of the requirements documents, each group member gained an understanding of what they were going to be responsible for. Each member also got a feel for what the other members strengths were, and how they could be allocated to further the group's progress towards the project's completion.
   & 
   Each member, having gained a deeper understanding of their portion of the project, was given a sense of ownership of their portion of the project. This ownership defines what each member's role in the project is. Each member now has a sense of what their future objectives will involve and what can be expected from them.
   \\
   \hline
\end{tabular}

\section{Week 8}

\subsection{Summary}

The group continued to work on the Technology Review, and conversed about each group 
member's role in the project based on research areas for the review. Chien's research 
is on media streaming, image processing, and data storage. Smedley's research is on 
development technologies in the Jetson TX1 and TX2, system interfaces, and operating 
systems. Striby's research is on SoMs, carrier boards, and camera cases for mounting. \\

Hardware arrived and the group coordinated with McGrath to obtain everything. Carlo was 
informed of all hardware ordered thus far and what the group had possession of. Smedley 
retrieved the Jetson TX2 SoM from Striby and began configuring the device. The group 
had their weekly Friday meeting with Lin.\\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   Each group member became more versed on the project's technologies and 
   began investigating the software development that will take place for the project. 
   Group members established their specialty areas for the project.  
   & 
   Setting up the TX2 for the first time gave Smedley more information about development technologies involved with the hardware, shedding light on future requirements. 
   & 
   The group discussed more specific details regarding system requirements and how they would be implemented. 
   \\
   \hline
\end{tabular}

\section{Week 9}

\subsection{Summary}

Each group member's Technical Review was completed and submitted. One Tuesday of Week 
9 the group had a virtual meeting with Carlo. During the meeting hardware procurement 
was the primary discussion, Smedley's progress with the Jetson TX2 was included, and 
a meeting over Winter Break was planned. Tiana inquired about hardware ordered and 
what the group has discovered for project development. The group's weekly meeting with 
Lin did not take place due to Thanksgiving Break. \\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   Technical Reviews were completed. A virtual meeting was held with Tiana. The 
   TX2 SoM had began being configured by Smedley.  
   & 
   Smedley had gained more knowledge about the TX2 and associated software. This information would be shared with the group so that each member could use it to further their progress in their respective portions of the project.
   & 
   The group met during class and shared knowledge pertaining to the project; each member gained an understanding of what their objectives were and how best to implement their knowledge into the project.
   changes \\
   \hline
\end{tabular}

\section{Week 10}

\subsection{Summary}

The group worked on The Software Design Description (SDD) throughout the week. Smedley 
researched hardware interfaces and system architecture. Chien researched image 
processing and video output. Striby researched pixel data processing and multimedia 
API. Help on details for the SDD were pursued and examples of prior SDDs were examined 
from previous Capstone projects. Immediately following submission of the SDD the 
group began working on the Progress Report. \\

Another hardware item ordered arrived and more hardware was ordered due to 
specifications discovered. The group now has three carrier boards and six cameras to 
continue project development over Winter Break. The group had their weekly Friday 
meeting with Lin.\\

\subsection{Retrospective}

\begin{tabular}{|p{0.3\linewidth}|p{0.3\linewidth}|p{0.3\linewidth}|}
   \hline
   \textbf{Positives} & \textbf{Deltas} & \textbf{Actions}\\ 
   \hline
   The SDD was completed and many software design concerns were discovered. The group 
   has lots of work to be done over Winter Break to learn more about how to develop 
   the project's software.  
   & 
   Cameras need to be connected to the TX2 in order to test connectivity and compatibility of the involved hardware. The group also needs to learn how to interface with the cameras using software.
   & 
   During Winter break, the group will attempt to connect two cameras to the system and establish a data transmission from each camera to a screen and verify that each camera works independently. Each group member will be expected to contribute knowledge and some work to meet this goal.
   \\
   \hline
\end{tabular}


\nocite{*}

\end{document}