\subsection{Problem}
% talk about 1) what's being requested, 2) who requested it & why, what is its importance
% 2-3 paragraphs, minimum

Our project is required to provide a video output at near real-time from a 
multi-camera input utilizing an NVIDIA Jetson TX2 system-on-module (SoM). 
The project is intended for UAS (Unmanned Aerial Systems) and VR/AR applications, 
and the requirements were established by Carlo Tianna of Rockwell Collins. 
The software produced is requested to perform image processing and edge computing on the 
camera input to display a stitched and tiled video output.  \\

Specific size, weight, power, and cost (SWaP-C) contraints that were required of our 
product established a certain path for the project. Due to the project's applications  
the hardware for the project had to be light-weight and compact, and have a low power 
draw. Therefore, it was specified that the product utilize the Jetson TX2 without its 
development kit and instead with a compatible carrier board. Our cost constraint is 
met by the hardware being off-the-shelf, and the software developed using free 
open-source programming libraries, multimedia framework, and operating system.  \\

Another hardware requirement established by our client was that the cameras used in
the project utilize a CSI (cameral serial interface) for its input specification to our 
carrier board due to how fast it is capable of transferring image data to the Jetson TX2. 
This requirement therefore influenced our carrier board selection to support a CSI 
connection to the cameras in our final product.  \\

The importance of our project comes from the cost constraint established by our client. 
Mr. Tianna is seeking a low-cost product to perform image processing and edge computing 
through the use of off-the-shelf hardware and open-source software to reduce the cost 
of a fully developed and tested solution. The software requested to be developed for 
the project is giving our client a glimpse of the full potential when using the Jetson 
TX2. With our project Mr. Tianna has a better understanding of the capabilities of our 
hardware selected and other similar hardware.  \\

\subsection{Persons Involved and Their Role}
% talk about: 1) members of the team, roles, restate client & state his role
%Keith will do 

This project was worked on by Shu-Ping Chien, Brock Smedley, and Keith Striby. Chien 
focused on TX2 compatibility with the various carrier board and camera setups and image 
processing with OpenCV. Smedley focused on system software setup and writing scripts to 
to replicate our system software setup. Striby focused on researching and ordering 
the project's hardware, TX2 compatibility with the 
various carrier board and camera setups, GStreamer pipelines, and image processing with 
OpenCV. Each group member contributed to various forms of troubleshooting due to 
TX2 compatibility issues and to improve our software capabilities.  \\

The client of our project, Mr. Tianna, supervised the project and worked closely with the 
team over the duration of the 
academic school year. He established requirements and guided us to our 
product's expected results by providing goals use throughout the life of the project. \\