\subsubsection{What technical information did you learn?}
Since we had many attempts on many new hardware and software, I thought that I learned much through 
this project. At least I have known these technologies that I didn't know before after working in the
 project. We started to work on researching things on hardware, and I learned many new terms such as 
 CSI, TX2 module, motherboard and carrier board. By comparing advantage and disadvantage between these 
 technologies, I considered that it is really a complex thing when human invented and defined these. \\

 Then in the next step, we moved to the software part, and it was more familiar for computer science 
 student even though there were still many things required us to search on. I thought that the pipeline 
 system GStreamer was a cool thing in our project, although I only looked on the usage about NVIDIA cameras. 
 Also, it was interesting to program with OpenCV and the cmake compiler during the project. \\

\subsubsection{What non-technical information did you learn?}
Through this project, I thought that the connection between hardware devices was more complicated than
 I thought before that we were not able to write a driver for TX2 and carrier board. On the other hand, 
 I considered that a group really need a leader to lead a group to trace the current process and 
 distribute work. Also, I felt comfortable to ask questions when collaborate in my group that I didn't 
 like to do this before. \\

\subsubsection{What have you learned about project work?}
I was surprised to know that sometimes a project may not have a specific goal or outline, so I felt like 
that we spent a lot of time on determining what we would like to use in our project. Then after we 
chose all potential technologies, we also need to explore on how to use it, and it was terrible 
if one failed. \\

\subsubsection{What have you learned about project management?}
In our experience for the project, things started to be late since the setup work on TX2 environment was 
more difficult than in our initial plan. Therefore, I considered that it was important to determine the 
most important goal in a project and work on it once there was any accident. In our project, we regarded 
the latency of image capturing and processing as our majority goal. \\

\subsubsection{What have you learned about working in teams?}
It was nice if you knew that who was good at what area, so the collaboration would be more influence. 
I also learned the way to work people whose personality was very different with each team member, different 
pace, different opinions, and different preference to work. Therefore, communication would be very important 
in a team to know how every one was working on. \\

\subsubsection{If you could do it all over, what would you do differently?}
Since we was stopped on hardware setup for a long time, and each time we reflashed the TX2 module would 
take around a couple hours, it may be better if we looked on software or other potential boards earlier. 
Although I thought that it was not an easy thing to change on different device immediately because we have 
already spent much time on the thing at that time. \\